Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
Added ppi

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")

@@

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, popu) %>%
  mutate(model = "cp") %>%
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model) %>% 
              mutate(model = "pp")) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn, popu) %>%
              mutate(model = paste0("np_", popu))) %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "np_1", "np_2", "np_3"))) -> disp_df

>>>>

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")
load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")

@@

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, popu) %>%
  mutate(model = "cp") %>%
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model) %>% 
              mutate(model = "pp")) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn, popu) %>%
              mutate(model = paste0("np_", popu))) %>% 
  bind_rows(., ppi.summ.df %>% 
              dplyr::select(av.disp, dsprsn, model) %>% 
              mutate(model = "ppi")) %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "ppi","np_1", "np_2", "np_3"))) -> disp_df
